Block bootstrap consistency\\under weak assumptions

### 2017-04-05 Paper.tex
Make very minor tweaks to wording during review

To prove~\eqref{eq:19}, it suffices (via the LIE and Lemma~\ref{L2})
to show that
\begin{equation*}
  \sum_{j=1}^{J_n} \Em \big ( Z_{nj}^{*2} \ind \{ Z_{nj}^{*2} > \epsilon \} \big ) \to^p 0.
\end{equation*}
But note that
\begin{equation*}
  \sum_{j=1}^{J_n} \Em \big ( Z_{nj}^{*2} \ind \{ Z_{nj}^{*2} > \epsilon \} \big )
  \leq \max_{j=1,\dots,J_n} \Em \big ( \tfrac{ n }{ M_{nj} } Z_{nj}^{*2}
  \ind \{ \tfrac{ n }{ M_{nj} } Z_{nj}^{*2} >
  \min_{k=1,\dots,J_n} \tfrac{ n }{ M_{nk} } \epsilon \} \big )
\end{equation*}
almost surely. Lemmas~\ref{L1} and~\ref{L6} imply that the RHS converges to
zero in probability as $n \to \infty$
proving~\eqref{eq:19}. The Dominated Convergence Theorem and~(\ref{eq:18})
then ensure that
\begin{equation}\label{eq:22}
  \pr^{*} \Big[\sum_{j=1}^{J_n}
  Z_{nj}^{*} / \sigma_n^* \leq x \Big] - \Phi(x) \to^p 0.
\end{equation}
(Also see
Lemma~\ref{L2}.)

@@

For~\eqref{eq:9}, fix $\delta> 0$ such that $D = 2/\delta$ is a
positive integer and let $\gamma_d = d/D$ for $d =
0,\dots,D$. Mimicking the argument in \cite{JoD:00b} gives the bounds
\begin{align*}
  \pr[\sup_{\gamma \in [0,1]} &
  \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
  | W_n^{*}(\gamma) - W_n^{*}(\gamma') | > \epsilon] \\
  &\leq \pr[ \sup_{d = 1,\dots,D} \sup_{\gamma \in [0,\delta]}
  | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) | > \epsilon/2] \\
  &\leq  (4/\epsilon^2) \sum_{d=1}^D \E[\sup_{\gamma \in [0,\delta]}
  | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 \\
  &\qquad\qquad\qquad \times \ind\{\sup_{\gamma \in [0,\delta]}
  | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > \epsilon^2/4\}] \\
  &\leq  (4/\epsilon^2) \max_{d=1,\dots,D} \E[\sup_{\gamma \in [0,\delta]}
  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 \\
  &\qquad\qquad\qquad \times \ind\{\sup_{\gamma \in [0,\delta]}
  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > \epsilon^2/4\delta\}].
\end{align*}
Lemma~\ref{L6} implies that
\begin{equation*}
  \sup_{\gamma \in [0,\delta]}
  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2
\end{equation*}
is uniformly integrable, so an argument similar to that used in the
proof of Theorem~\ref{T1} shows that there exists a
finite and monotone function $B$ such that $B(x) \to 0$ as
$x \to \infty$ and
\begin{multline*}
  \E[\sup_{\gamma \in [0,\delta]}
  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 \times \\
  \ind\{\sup_{\gamma \in [0,\delta]}
  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > x\}]
  \leq B(x)
\end{multline*}
for all $d$ and $\delta$ and all large enough $n$.

As a result,
\begin{align*}
  \lim_{\delta \to 0} \limsup_{n\to\infty} \pr[\sup_{\gamma \in [0,1]}
  \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
  | W_n^{*}(\gamma) - W_n^{*}(\gamma') | > \epsilon] & \leq
  \lim_{\delta \to 0} (4/\epsilon^2)
  B(\epsilon^2/4\delta) \\
  &= 0,
\end{align*}
completing the proof.\qed

@@

  For any $x$, define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
  \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$
  into a summation of conditionally independent blocks, giving
  \begin{multline} \label{eq:42}
    Z^{*}_n(\tau, m) = Z_n^*(\tau, K_{n,J(\tau)} - \tau) +
    \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* \\
    + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}).
  \end{multline}
  Since the distribution of $Z_n^*(\tau, m)$ does not depend on
  $\tau$, \eqref{eq:30} holds if, for any positive $\epsilon$ and
  $\epsilon'$, there exist $n_0$ and $C_0$ such that
  \begin{multline} \label{eq:31}
    \Pr \big [ \max_{\tau=0,\dots,n-1}
    \Em \big ( ( \max_{ m = 1, \dots, K_{n,J(\tau)} - \tau} n \, Z^*_n(\tau, m)^2 / M_{n,J(\tau)} ) \\
    \times \ind \{ \max_{ m = 1, \dots, K_{n,J(\tau)} - \tau} n \, Z^*_n(\tau, m)^2 / M_{n,J(\tau)} > C \}
    \big ) > \epsilon \big ] < \epsilon',
  \end{multline}
  \begin{multline} \label{eq:44}
    \pr \Big [
    \max_{m'=1,\dots,n}
    \Em \Big (
    \tfrac{n}{m'} \max_{k=1,\dots,J(m')} \Big\lvert \sum_{j=1}^{k} Z_{nj}^* \Big\rvert^2 \\
    \times \ind \Big \{
    \tfrac{n}{m'} \max_{k=1,\dots,J(m')} \Big\lvert \sum_{j=1}^{k} Z_{nj}^* \Big\rvert^2
    > C \Big \} \Big ) > \epsilon \Big ] < \epsilon'
  \end{multline}
  and
  \begin{multline} \label{eq:5}
    \Pr \big [ \max_{j=1,\dots,J_n}
    \Em \big ( ( \max_{ m = 1, \dots, M_{nj}} n \, Z^*_n(K_{n,j-1}, m)^2 / M_{nj} ) \\
    \times \ind \{ \max_{ m = 1, \dots, M_{nj}} n \, Z^*_n(K_{n,j-1}, m)^2 / M_{nj} > C \}
    \big ) > \epsilon \big ] < \epsilon',
  \end{multline}
  for all $n > n_0$ and $C > C_0$.

>>>>

To prove~\eqref{eq:19}, it suffices (via the LIE and Lemma~\ref{L2})
to show that
\begin{equation*}
  \sum_{j=1}^{J_n} \Em \big ( Z_{nj}^{*2} \ind \{ Z_{nj}^{*2} > \epsilon \} \big ) \to^p 0.
\end{equation*}
But note that
\begin{equation*}
  \sum_{j=1}^{J_n} \Em \big ( Z_{nj}^{*2} \ind \{ Z_{nj}^{*2} > \epsilon \} \big )
  \leq \max_{j=1,\dots,J_n} \Em \big ( \tfrac{ n }{ M_{nj} } Z_{nj}^{*2}
  \ind \{ \tfrac{ n }{ M_{nj} } Z_{nj}^{*2} >
  \min_{k=1,\dots,J_n} \tfrac{ n }{ M_{nk} } \epsilon \} \big )
\end{equation*}
almost surely. Lemmas~\ref{L1} and~\ref{L6} imply that the RHS converges to
zero in probability as $n \to \infty$,
proving~\eqref{eq:19}. The Dominated Convergence Theorem and~(\ref{eq:18})
then ensure that
\begin{equation}\label{eq:22}
  \pr^{*} \Big[\sum_{j=1}^{J_n}
  Z_{nj}^{*} / \sigma_n^* \leq x \Big] - \Phi(x) \to^p 0.
\end{equation}
(Also see
Lemma~\ref{L2}.)

@@

For~\eqref{eq:9}, fix $\delta> 0$ such that $D = 2/\delta$ is a
positive integer and let $\gamma_d = d/D$ for $d =
0,\dots,D$. Mimicking the argument in \cite{JoD:00b} gives the bounds
\begin{align*}
  \pr[\sup_{\gamma \in [0,1]} &
  \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
  | W_n^{*}(\gamma) - W_n^{*}(\gamma') | > \epsilon] \\
  &\leq \pr[ \sup_{d = 1,\dots,D} \sup_{\gamma \in [0,\delta]}
  | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) | > \epsilon/2] \\
  &\leq  (4/\epsilon^2) \sum_{d=1}^D \E[\sup_{\gamma \in [0,\delta]}
  | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 \\
  &\qquad\qquad\qquad \times \ind\{\sup_{\gamma \in [0,\delta]}
  | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > \epsilon^2/4\}] \\
  &\leq  (4/\epsilon^2) \max_{d=1,\dots,D} \E[\sup_{\gamma \in [0,\delta]}
  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 \\
  &\qquad\qquad\qquad \times \ind\{\sup_{\gamma \in [0,\delta]}
  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > \epsilon^2/4\delta\}]
\end{align*}
for large enough $n$. Lemma~\ref{L6} implies that
\begin{equation*}
  \sup_{\gamma \in [0,\delta]}
  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2
\end{equation*}
is uniformly integrable, so
\begin{multline*}
  \lim_{\delta \to 0} \limsup_{n\to\infty}\
  \max_{d=1,\dots,D}
  \E[\sup_{\gamma \in [0,\delta]} (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2
  \times \\
  \ind\{\sup_{\gamma \in [0,\delta]}
  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > \epsilon^2/4\delta\}]
  = 0,
\end{multline*}
completing the proof.\qed

@@

  For any $x$, define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
  \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$
  into a summation of conditionally independent blocks
  \begin{multline} \label{eq:42}
    Z^{*}_n(\tau, m) = Z_n^*(\tau, K_{n,J(\tau)} - \tau) +
    \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* \\
    + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}).
  \end{multline}
  Since the distribution of $Z_n^*(\tau, m)$ does not depend on
  $\tau$, \eqref{eq:30} holds if, for any positive $\epsilon$ and
  $\epsilon'$, there exist $n_0$ and $C_0$ such that
  \begin{multline} \label{eq:31}
    \Pr \big [ \max_{\tau=0,\dots,n-1}
    \Em \big ( ( \max_{ m = 1, \dots, K_{n,J(\tau)} - \tau} n \, Z^*_n(\tau, m)^2 / M_{n,J(\tau)} ) \\
    \times \ind \{ \max_{ m = 1, \dots, K_{n,J(\tau)} - \tau} n \, Z^*_n(\tau, m)^2 / M_{n,J(\tau)} > C \}
    \big ) > \epsilon \big ] < \epsilon',
  \end{multline}
  \begin{multline} \label{eq:44}
    \pr \Big [
    \max_{m'=1,\dots,n}
    \Em \Big (
    \tfrac{n}{m'} \max_{k=1,\dots,J(m')} \Big\lvert \sum_{j=1}^{k} Z_{nj}^* \Big\rvert^2 \\
    \times \ind \Big \{
    \tfrac{n}{m'} \max_{k=1,\dots,J(m')} \Big\lvert \sum_{j=1}^{k} Z_{nj}^* \Big\rvert^2
    > C \Big \} \Big ) > \epsilon \Big ] < \epsilon'
  \end{multline}
  and
  \begin{multline} \label{eq:5}
    \Pr \big [ \max_{j=1,\dots,J_n}
    \Em \big ( ( \max_{ m = 1, \dots, M_{nj}} n \, Z^*_n(K_{n,j-1}, m)^2 / M_{nj} ) \\
    \times \ind \{ \max_{ m = 1, \dots, M_{nj}} n \, Z^*_n(K_{n,j-1}, m)^2 / M_{nj} > C \}
    \big ) > \epsilon \big ] < \epsilon',
  \end{multline}
  for all $n > n_0$ and $C > C_0$.
